---
title: "Bike Hire Report"
author: "Richard"
date: "02/09/2021"
output: pdf_document
---

```{r setup, include=FALSE}

#set options to stop R code showing in final report
knitr::opts_chunk$set(echo = FALSE)

#Load Libraries
library(dplyr)
library(ggplot2)
library(caret)
library(corrplot)
```

# Bike Hire Scheme Project

## Executive Summary

This report presents a summary of a project completed as the final part of the **HarvardX Data Science Program**. The project uses the data analysis and R programming skills learned during the program to estimate the ratings given to movies based on a range of predictors.

The project uses a dataset of 10 million ratings of movies. All movies are given a rating between 0 and 5. The aim of the project is to develop a methodology and R code which correctly predicts the rating a movie will receive.

The methodology I developed uses a range of predictors to estimate the rating a movie will receive. The starting point for the prediction is the average rating across all movies, this is:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
